Solving the maximum independant set problem by generic programming einsum networks \thanks{\funding{...}}

### 2021-07-30 paper/paper.tex

\section{Introduction}
MIS problem is hard~\cite{Hastad1996}.
Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $2^{tw(G)}$.
A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
A set is independent if and only if its complement is a vertex cover. Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
It is related to hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.

@@

>>>>

% REQUIRED
\begin{keywords}
  maximum independent set, einsum network
\end{keywords}

% REQUIRED
% 14N07  	Secant varieties, tensor rank, varieties of sums of powers
\begin{AMS}
  05C31, 14N07
\end{AMS}

\section{Introduction}
MIS problem is hard~\cite{Hastad1996}.
Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $O(2^{tw(G)}tw(G)n)$.
A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
A set is independent if and only if its complement is a vertex cover. Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
It is related to hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.

@@

\section{matching polynomial}
One can generalize the generic einsum network for solving another \#P-complete problem, the matching polynomials.
A match polynomial of a graph $G$ is defined as
\begin{align}
    M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
\end{align}
where $k$ is the number of matches, and coefficients $c_k$ are countings.

We define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
\begin{align}
    W_{v\rightarrow n_1, v\rightarrow n_2, \ldots, v\rightarrow n_{d(v)}} = \begin{cases}
        1, & \sum_{i=1}^{d(v)} v\rightarrow n_i \leq 1,\\
        0, & otherwise,
    \end{cases}
\end{align}
and a tensor of rank $1$ on the bond
\begin{align}
    B_{v\rightarrow w} = \begin{cases}
    1, & v \rightarrow w = 0 \\
    x, & v \rightarrow w = 1.
\end{cases}
\end{align}

Here, we use bond index $v \rightarrow w$ to label tensors.
